Supervised Reinforcement Learning with Partial States: \\ a Teaching Method for Action Selection for HRI

### 2017-07-18 paper.tex
End of first pass

Other way of extending the current work would be to combine it with the
possibility of letting the agent continue to explore in the absence of a
supervisor around a learnt action policy to keep improving its behaviour. This
could be done by allowing the supervisor to provide rewards during the learning
phase, rewards which could also be assigned to partial states. The system could
also learn to predict these rewards in an approach similar to TAMER 
\cite{knox2009interactively}. But in the case of an absence of supervisor, the assumption that only a
myopic action selection is sufficient would not hold anymore and the problem of
delayed rewards would have to be tackled. It could be for example possible to
adapt well known algorithms such as QLearning to handle partial states rather
the full states.

%===============================================================================
\section{Conclusion}
\label{sec:conclusion}
%==============================================================================
\section{Acknowledgments}
This work was supported by the EU FP7 DREAM project (grant no.  611391) and EU
H2020 Marie Sklodowska-Curie Actions project DoRoThy (grant 657227).

>>>>

The current work could be extended to allow the agent continue to improve its
behaviour even in the absence of supervisor, exploring around a learnt policy
progressively improving its policy beyond what have been taught. This
could be done by allowing the supervisor to provide rewards during the learning
phase, and combine these rewards with the demonstrations to learn a reward
function in a fashion similar to Inverse Reinforcement Learning
\cite{abbeel2004apprenticeship}. These could also use partial states associated
to these rewards to have a general reward function despite a low number of
datapoints.
But without the supervisor, the assumption that only a
myopic action selection is sufficient would not hold anymore and the problem of
delayed rewards would have to be tackled.
%===============================================================================
\section{Conclusion}
\label{sec:conclusion}
%==============================================================================
\section{Acknowledgments}
This work was supported by the EU FP7 DREAM project (grant no.  611391) and EU
H2020 Marie Sklodowska-Curie Actions project DoRoThy (grant 657227).
